My title

### 2024-03-08 paper/paper.qmd
^

@@

```{r}
modelplot(political_preferences2, conf_level = 0.9) +
  labs(x = "90 per cent credibility interval")
```

>>>>

political_preferences3 <-
  readRDS(file = here::here("models/political_preferences3.rds"))

political_preferences4 <-
  readRDS(file = here::here("models/political_preferences4.rds"))

political_preferences5 <-
  readRDS(file = here::here("models/political_preferences5.rds"))

political_preferences6 <-
  readRDS(file = here::here("models/political_preferences6.rds"))

political_preferences7 <-
  readRDS(file = here::here("models/political_preferences7.rds"))

political_preferences8 <-
  readRDS(file = here::here("models/political_preferences8.rds"))

political_preferences9 <-
  readRDS(file = here::here("models/political_preferences9.rds"))
```

@@

```{r}
modelsummary(
  list(
    "Support Biden" = political_preferences3
  ),
  statistic = "mad"
  )
```

```{r}
modelsummary(
  list(
    "Support Biden" = political_preferences4
  ),
  statistic = "mad"
  )
```
```{r}
modelsummary(
  list(
    "Support Biden" = political_preferences5
  ),
  statistic = "mad"
  )
```
```{r}
modelsummary(
  list(
    "Support Biden" = political_preferences6
  ),
  statistic = "mad"
  )
```
```{r}
modelsummary(
  list(
    "Support Biden" = political_preferences7
  ),
  statistic = "mad"
  )
```
```{r}
modelsummary(
  list(
    "Support Biden" = political_preferences8
  ),
  statistic = "mad"
  )
```

```{r}
modelsummary(
  list(
    "Support Biden" = political_preferences9
  ),
  statistic = "mad"
  )
```

```{r}
modelplot(political_preferences9, conf_level = 0.9) +
  labs(x = "90 per cent credibility interval")
```
